Reactor Design Compilation

### 2019-07-02 msr-list.tex
adding table text, changing text where tables have covered information

\documentclass[letterpaper]{article}
\usepackage[top=1.0in,bottom=1.0in,left=1.0in,right=1.0in]{geometry}
\usepackage{verbatim}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{svg}
\usepackage{longtable}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{float}
\usepackage{caption}
\usepackage{xcolor}
\def\thesection       {\arabic{section}}
\def\thesubsection     {\thesection.\alph{subsection}}

@@

\section{Introduction}
Molten salt reactors, or MSRs, are a hopeful candidate for the next line of commerical nuclear reactors.  However, there is a lack of experiental data and real-world experience compared to the light-water reactors that make up much of the world's current fleet.***say more words here later***

To begin, take note of \cite{macpherson_molten_1985} and \cite{rosenthal_molten-salt_1970}.  These articles are not specific designs, instead, they give a general history of US MSR technology up to approximately 1980.  \cite{macpherson_molten_1985}, in particular, is a personal account of the author's experience in the growing field, and offers interesting insight.\\

This report seeks to collect various MSR designs and reprocessing techniques, and from them, provide an idea of the range of MSR features.  The intent is to capture the expected varieties of fluid-fueled MSRs such that models and simulations can accommodate a broad range of designs.  The features given in this review include characteristics such as:

@@

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
MWth & value \\
\hline
MWe & value \\
\hline
Spectrum & value \\
\hline
Core Inlet Temperature & value \\
\hline
Core Outlet Temperature & value\\
\hline
Pressure & value \\
\hline
\end{tabular}
\end{center}

\begin{itemize}
\item Heat generation of 10 MWth
\item Single-region
\item Graphite moderator
\item Fuel salt is a mix of lithium, beryllium, and zirconium fluoride salts, using either uranium or uranium and thorium.  Specifics of the composition are given in Table 2.1 of \cite{robertson_msre_1965}.
\item Total core volume is 90 cubic feet.  20 cubic feet is fuel, 70 cubic feet is graphite.
\item Graphite matrix is set in a rectangular grid, with 6 holes taken out to hold control rods.
\end{itemize}

@@

There is not "online" reprocessing in this design, exactly.  When the fuel salts have become contaminated or otherwise undesireable, they are removed from the reactor, which is then flushed with a "flush salt".  This flush salt is simply the fuel salt mixture without any of the fissile isotopes added.

After chemical treatment, what can be saved from the salt is reused, the rest is disposed of.

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
MWth & value \\
\hline
MWe & value \\
\hline
Spectrum & value \\
\hline
Core Inlet Temperature & value \\
\hline
Core Outlet Temperature & value\\
\hline
Pressure & value \\
\hline
\end{tabular}
\end{center}

@@

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
MWth & value \\
\hline
MWe & value \\
\hline
Spectrum & value \\
\hline
Core Inlet Temperature & value \\
\hline
Core Outlet Temperature & value\\
\hline
Pressure & value \\
\hline
\end{tabular}
\end{center}

@@

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
MWth & value \\
\hline
MWe & value \\
\hline
Spectrum & value \\
\hline
Core Inlet Temperature & value \\
\hline
Core Outlet Temperature & value\\
\hline
Pressure & value \\
\hline
\end{tabular}
\end{center}

@@

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
MWth & value \\
\hline
MWe & value \\
\hline
Spectrum & value \\
\hline
Core Inlet Temperature & value \\
\hline
Core Outlet Temperature & value\\
\hline
Pressure & value \\
\hline
\end{tabular}
\end{center}

@@

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
MWth & value \\
\hline
MWe & value \\
\hline
Spectrum & value \\
\hline
Core Inlet Temperature & value \\
\hline
Core Outlet Temperature & value\\
\hline
Pressure & value \\
\hline
\end{tabular}
\end{center}

@@

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
MWth & value \\
\hline
MWe & value \\
\hline
Spectrum & value \\
\hline
Core Inlet Temperature & value \\
\hline
Core Outlet Temperature & value\\
\hline
Pressure & value \\
\hline
\end{tabular}
\end{center}

@@

\section{Terrapower}
website \href{https://terrapower.com/technologies/mcfr}{here}

Much of the current information about Terrapower's designs are in patents, and, therefore, not given in exact detail \cite{hyde_liquid_2015}.  However, it can be said that:

\begin{center}
\begin{tabular}{|c|c|}
\hline
MWth & value \\
\hline
MWe & value \\
\hline
Spectrum & value \\
\hline
Core Inlet Temperature & value \\
\hline
Core Outlet Temperature & value\\
\hline
Pressure & value \\
\hline
\end{tabular}
\end{center}

\begin{itemize}
\item The core has two regions, one fissile, one a fertile blanket.  The patent does not specify how exactly these regions are arranged, and also gives a homogenous mixture of the two materials as a possibility
\item ${}^{239}Pu$ is given as a possible isotope present in the fissile region, and ${}^{238}U$ as the fertile isotope in the fertile blanket
\end{itemize}

\bibliographystyle{plain}
\bibliography{2019-richter-msr-litrev}
\end{document}

>>>>

\documentclass[letterpaper]{article}
\usepackage[top=1.0in,bottom=1.0in,left=1.0in,right=1.0in]{geometry}
\usepackage{verbatim}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{svg}
\usepackage{longtable}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{float}
\usepackage{caption}
\usepackage{xcolor}
\usepackage{makecell}
\def\thesection       {\arabic{section}}
\def\thesubsection     {\thesection.\alph{subsection}}

@@

\section{Introduction}
Molten salt reactors, or MSRs, are a hopeful candidate for the next line of commerical nuclear reactors.  However, there is a lack of experiental data and real-world experience compared to the light-water reactors that make up much of the world's current fleet.

This report seeks to collect various MSR designs and reprocessing techniques, provide an idea of the range of MSR features.  The intent is to capture the expected varieties of fluid-fueled MSRs such that models and simulations can accommodate a broad range of designs.  The features given in this review include characteristics such as:

@@

To begin, take note of \cite{macpherson_molten_1985} and \cite{rosenthal_molten-salt_1970}.  These articles are not specific designs, instead, they give a general history of US MSR technology up to approximately 1980. \emph{The Molten Salt Adventure}, \cite{macpherson_molten_1985}, in particular, is a personal account of the author's experience in the growing field, and offers interesting insight.\\

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
MWth & 10\\
\hline
MWe & Not Given \\
\hline
Spectrum & Thermal \\
\hline
Core Inlet Temperature & 635 C \\
\hline
Core Outlet Temperature & 663 C\\
\hline
Pressure & 0.14 MPa \\
\hline
\end{tabular}
\end{center}

\begin{itemize}
\item Single-region
\item Fuel salt is a mix of lithium, beryllium, and zirconium fluoride salts, using either uranium or uranium and thorium.  Specifics of the composition are given in Table 2.1 of \cite{robertson_msre_1965}.
\item Total core volume is 90 cubic feet.  20 cubic feet is fuel, 70 cubic feet is graphite.
\item Graphite matrix is set in a rectangular grid, with 6 holes taken out to hold control rods.
\end{itemize}

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
Fuel-Moderator Ratio & 22.4-77.6 \\
\hline
Coolant & $LiFBeF_2$ \\
\hline
Moderator & Graphite \\
\hline
Fuel Composition & 2, 3, 4 \\
\hline
\end{tabular}
\end{center}

The fuel processing in the MSRE is relatively straight-forward.  The helium cover gas used in the pump bowl will remove fission product gases.  Beyond the off-gas system, and further fuel processing is done batch-wise, not as part of the fuel loop.  This fuel processing system can:

\begin{itemize}
\item Treat batches of oxygen-contaminated fuel salts with a $H_2F$ gas to remove the oxygen
\item Can perform fluorination on batches of fuel salts.  This will separate the uranium from the salt mixture.  From this point, the salt is either sent to waste, or kept, and a new fuel is added to the batch.  This allows for both "cleaning" the fuel, or changing its composition considerably, in large quantities.
\end{itemize}

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
MWth & 2250 \\
\hline
MWe & 1000 \\
\hline
Spectrum & Thermal \\
\hline
Core Inlet Temperature & 566 C \\
\hline
Core Outlet Temperature & 704 C\\
\hline
Pressure & 0.52 MPa \\
\hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
Fuel-Moderator Ratio & 13-87 \\
\hline
Moderator & Graphite \\
\hline
Fuel Composition & 5 \\
\hline
Secondary Salt* & $NaBF_4-NaF$ \\
\hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
MWth & 750 \\
\hline
MWe & 350 \\
\hline
Spectrum & Thermal \\
\hline
Core Inlet Temperature & 566 C\\
\hline
Core Outlet Temperature & 677 C\\
\hline
Pressure & \makecell{Not given explicitly.  Assume\\pressure drop of 0.03 MPa across reflectors.\\Nothing in source to indicate core vessel\\pressure differs significantly from predecessors.} \\
\hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
Fuel-Moderator Ratio & 10-90 \\
\hline
Coolant & $LiFBeF_2$ \\
\hline
Moderator & Graphite \\
\hline
Fuel Composition & 6 \\
\hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
MWth & 2250 \\
\hline
MWe & 1000 \\
\hline
Spectrum & Thermal \\
\hline
Core Inlet Temperature & 566 C \\
\hline
Core Outlet Temperature & 704 C\\
\hline
Pressure & Not given \\
\hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
Fuel-Moderator Ratio: Inner Core & 20-80 \\
\hline
Fuel-Moderator Ratio: Outer Core & 12.94-87.06  \\
\hline
Coolant & $LiFBeF_2$ \\
\hline
Moderator & Graphite \\
\hline
Fuel Composition & 7 \\
\hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
MWth & 400 \\
\hline
MWe & 188 \\
\hline
Spectrum & Thermal \\
\hline
Core Inlet Temperature & 647 C \\
\hline
Core Outlet Temperature & 685 C\\
\hline
Pressure & 0.4 MPa \\
\hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
Fuel-Moderator Ratio & N/A \\
\hline
Coolant & Fluoride Salt \\
\hline
Moderator & Graphite \\
\hline
Fuel Composition & "Fluoride Fuel Salt" \\
\hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
MWth & 3000 \\
\hline
MWe & 1500 \\
\hline
Spectrum & Fast \\
\hline
Core Inlet Temperature & 625 C \\
\hline
Core Outlet Temperature & 730 C \\
\hline
Pressure & Not Given \\
\hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
Fuel-Moderator Ratio & 100-0 \\
\hline
Coolant & \makecell{As fuel salt, without\\fuel isotopes.} \\
\hline
Moderator & No moderator \\
\hline
Fuel Composition & 8, 9 \\
\hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
MWth & 1250 \\
\hline
MWe & 520 \\
\hline
Spectrum & Thermal \\
\hline
Core Inlet Temperature & Not Given \\
\hline
Core Outlet Temperature & 650 C\\
\hline
Pressure & "Near-Atmospheric" \\
\hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|c|c|}
\hline
Fuel-Moderator Ratio & Not Given \\
\hline
Coolant & $FLiNaK$ \\
\hline
Moderator & Zirconium Hydride \\
\hline
Fuel Composition & 10 \\
\hline
\end{tabular}
\end{center}

\bibliographystyle{plain}
\bibliography{2019-richter-msr-litrev.bib}
\end{document}
